---
title: "FCTM_LabEx"
author: "L Burleigh"
date: "2022-11-17"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/larn_/OneDrive - Louisiana State University/R/FCTM_Bx_v1')
```

The FCTM_bx_v1 study consists of two tasks in which participants both view and imagine two Gabor patches in each set. In Set A (Imagery Acquisition), participants view and imagine a left-ward and vertical patch, and are fear conditioned when imagining one of these patches. In Set B (Visual Acquisition), participants view and imagine a right-ward and horizontal patch, and are fear conditioned when viewing one of these patches. These sets will be discussed in reverse (Set B: Visual Acquisition then Set A: Imagery Acquisition) for ease of understanding. 


These tasks allow for the investigation of 5 questions:

1. To determine if participants fear condition to a viewed stimulus

2. To determine if participants generalize this fear of a viewed stimulus to the corresponding imagined stimulus

3. To determine if participants fear condition to an imagined stimulus

4. To determine if participants generalize this fear to the corresponding viewed stimulus

5. To determine if the fear acquired when viewing a stimulus is of similar magnitude to the fear acquired when imagining a stimulus


This markdown is primarily to be used in order to determine which results to include in the main vs supplemental parts of the publication.
Contact L for questions: lburle2@lsu.edu or lburleigh09@gmail.com

```{r load data, include=FALSE}
# Load necessary libraries
library(tidyverse)
library(ggplot2) 
library(apaTables) 
library(condir) # Bayes
library(corrplot) 
library(effectsize)
library(ez) 
library(ggcorrplot) 
library(pastecs)
library(reshape)
library(ggpubr)

## This portion reads in the CSV and specifies participants to include in analyses

# setwd("C:/Users/larn_/OneDrive - Louisiana State University/R/FCTM_Bx_v1")
# setwd() here is unnecessary for knitting the markdown but is here for ease of troubleshooting
CSV <- read.csv("FCTM_Bx_df_stats.csv", header=TRUE, fileEncoding = "UTF-8")
keep <- c("16012", "16094", "17074", "17097", "17102", "17108", "17111", "17112", "17124", "17127", "17133", "17144", "17145", "17146", "17155", "17194", "17230", "17238", "17239", "17241", "17247", "17271", "17284", "17293", "17294", "17295", "17467", "17473", "17498", "17513", "17519", "18008", "18020")
CSV <- CSV[CSV$Subject_ID %in% keep, ]

```


# Likert-Style Questionnaire

## Descriptive Statistics

### Visual Acquisition (Set B) 

``` {r Likert VA, echo = FALSE}
CSVlikertVA <- CSV %>% select("B_vivid_Cspi", "B_vivid_Csmi", "B_effort_Cspi", "B_effort_Csmi", "B_fear_Cspi", "B_fear_Csmi", "B_fear_Cspv", "B_fear_Csmv")

likertVA <- stat.desc(CSVlikertVA)
print(likertVA)
```
### Imagery Acquisition (Set A) 

``` {r Likert IA, echo = FALSE}
CSVlikertIA <- CSV %>% select("A_vivid_Cspi", "A_vivid_Csmi", "A_effort_Cspi", "A_effort_Csmi", "A_fear_Cspi", "A_fear_Csmi", "A_fear_Cspv", "A_fear_Csmv")

likertIA <- stat.desc(CSVlikertIA)
print(likertIA)
```

## Analyses

### Subjective Fear ANOVA

``` {r, lik org, include = FALSE}
longCSVlik <- CSV %>% select("Subject_ID", "A_fear_Cspv", "A_fear_Csmv",	"A_fear_Cspi",	"A_fear_Csmi","B_fear_Cspv", "B_fear_Csmv", "B_fear_Cspi", "B_fear_Csmi") %>%
  pivot_longer(cols = c("A_fear_Cspv", "A_fear_Csmv",	"A_fear_Cspi",	"A_fear_Csmi","B_fear_Cspv", "B_fear_Csmv", "B_fear_Cspi", "B_fear_Csmi"),
               names_to = "groups", values_to = "data") %>%
  mutate(CS = case_when(grepl("Csp", groups) ~ "CSP",
                        grepl("Csm", groups) ~ "CSM")) %>%
  mutate(Percept = case_when(endsWith(groups, "v") ~ "View",
                             endsWith(groups, "i") ~ "Imagine")) %>%
  mutate(Phase = case_when(startsWith(groups, "A") ~ "A",
                           startsWith(groups, "B") ~ "B"))
```

```{r lik aov, echo = FALSE}
anovatbl <- ezANOVA(data=longCSVlik, dv = .(data), wid = .(Subject_ID), within = .(CS, Percept, Phase), type = 2, detailed = TRUE)

table1 <- apa.ezANOVA.table(anovatbl, table.number = 1, filename = "likertanova.doc")
print(anovatbl)
```



### Visualization
```{r b lik graph, echo=FALSE}
longB <- longCSVlik %>% filter(Phase == "B")

blik <- ggplot(longB, aes(CS, data, fill= CS)) 
blik <- blik + theme_bw() + stat_summary(fun = mean, geom = "bar", colour="Black") + stat_summary(fun.data =mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .35) + scale_x_discrete(breaks=c("CSP","CSM"), labels = c("CS+","CS-")) + scale_fill_manual(values=c("#D43F3A", "#357EBD")) + labs(y = "Self-Reported Fear (1-7)", size = "N") + theme(axis.title.x = element_blank(), text = element_text(size=20)) + facet_grid(cols = vars(Percept)) + geom_count(color = "gray36") + theme(legend.position="none")

ggsave(filename = "lik_VisAcq.tiff", plot = blik, height = 12, width = 11.6, units = "cm", device='tiff', dpi=300)

longA <- longCSVlik %>% filter(Phase == "A")

alik <- ggplot(longA, aes(CS, data, fill= CS)) 
alik <- alik + theme_bw() + stat_summary(fun = mean, geom = "bar", colour="Black") + stat_summary(fun.data =mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .35) + scale_x_discrete(breaks=c("CSP","CSM"), labels = c("CS+","CS-")) + scale_fill_manual(values=c("#EEA236", "#46B8DA"))  + theme(axis.title.x = element_blank(), text = element_text(size=20), axis.title.y = element_blank()) + facet_grid(~factor(Percept, levels=rev(unique(longA$Percept)))) + geom_count(color = "gray36") + guides(fill = "none")

ggsave(filename = "Lik_ImgAcq.tiff", plot = alik, height = 12, width = 11.6, units = "cm", device='tiff', dpi=300)

bothlik <- ggarrange(blik, alik, 
            widths = c(0.5, .75),
          ncol = 2, nrow = 1)
ggsave(filename = "Lik_both.tiff", plot = bothlik, height = 10, width = 24, units = "cm", device='tiff', dpi=300)
ggsave(filename = "Lik_both.png", plot = bothlik, height = 10, width = 24, units = "cm", device='png', dpi=300)

print(bothlik)
```


\pagebreak
# Three-way ANOVA Self-Report Follow-up tests

## Visual Acquisition Primary Analyses (Set B)

### Fear View
```{r}
t.test(data ~ groups, data = subset(longB, groups %in% c("B_fear_Cspv", "B_fear_Csmv")), paired=TRUE)
cohens_d(longB$data[longB$groups == "B_fear_Cspv"], longB$data[longB$groups == "B_fear_Csmv"], paired = TRUE)
```

#### Bayesian Test
```{r, echo = FALSE}
comp <- csCompare(CSV$B_fear_Cspv, CSV$B_fear_Csmv)
comp
interpret_bf(comp$bayes.results$bf10, include_value = TRUE)
```

Sensitivity + Robustness
```{r, echo = FALSE}
sens <- csSensitivity(CSV$B_fear_Cspv, CSV$B_fear_Csmv)
sens
csRobustnessPlot(CSV$B_fear_Cspv, CSV$B_fear_Csmv, BF01 = TRUE)
```


### Generalized Fear to Imagine
```{r}
t.test(data ~ groups, data = subset(longB, groups %in% c("B_fear_Cspi", "B_fear_Csmi")), paired=TRUE)
cohens_d(longB$data[longB$groups == "B_fear_Cspi"], longB$data[longB$groups == "B_fear_Csmi"], paired = TRUE)
```

#### Bayesian Test
```{r, echo = FALSE}
compi <- csCompare(CSV$B_fear_Cspi, CSV$B_fear_Csmi)
compi
interpret_bf(compi$bayes.results$bf10, include_value = TRUE)
```

Sensitivity + Robustness
```{r, echo = FALSE}
sens <- csSensitivity(CSV$B_fear_Cspi, CSV$B_fear_Csmi)
print(sens)
csRobustnessPlot(CSV$B_fear_Cspi, CSV$B_fear_Csmi, BF01 = TRUE)
```

## Imagery Acquisition Primary Analyses (Set A)

### Fear Imagine
```{r}
t.test(data ~ groups, data = subset(longA, groups %in% c("A_fear_Cspi",	"A_fear_Csmi")), paired=TRUE)
cohens_d(longA$data[longA$groups == "A_fear_Cspi"], longA$data[longA$groups == "A_fear_Csmi"], paired = TRUE)
```

#### Bayesian Test
```{r, echo = FALSE}
compi <- csCompare(CSV$A_fear_Cspi, CSV$A_fear_Csmi)
compi
interpret_bf(compi$bayes.results$bf10, include_value = TRUE)
```

Sensitivity + Robustness
```{r, echo = FALSE}
sensi <- csSensitivity(CSV$A_fear_Cspi, CSV$A_fear_Csmi)
print(sensi)
csRobustnessPlot(CSV$A_fear_Cspi, CSV$A_fear_Csmi, BF01 = TRUE)
```

### Generalized Fear to View
```{r}
t.test(data ~ groups, data = subset(longA, groups %in% c("A_fear_Cspv", "A_fear_Csmv")), paired=TRUE)
cohens_d(longA$data[longA$groups == "A_fear_Cspv"], longA$data[longA$groups == "A_fear_Csmv"], paired = TRUE)
```

#### Bayesian Test
```{r, echo = FALSE}
comp <- csCompare(CSV$A_fear_Cspv, CSV$A_fear_Csmv)
comp
interpret_bf(comp$bayes.results$bf10, include_value = TRUE)
```

Sensitivity + Robustness
```{r, echo = FALSE}
sens <- csSensitivity(CSV$A_fear_Cspv, CSV$A_fear_Csmv)
print(sens)
csRobustnessPlot(CSV$A_fear_Cspv, CSV$A_fear_Csmv, BF01 = TRUE)
```

## Visual Acquisition Additional follow-ups (Set B)

### CS+s
```{r}
t.test(data ~ groups, data = subset(longCSVlik, groups %in% c("B_fear_Cspi", "B_fear_Cspv")), paired=TRUE)
cohens_d(longCSVlik$data[longCSVlik$groups == "B_fear_Cspi"], longCSVlik$data[longCSVlik$groups == "B_fear_Cspv"], paired = TRUE)
```

### CS-s 
```{r}
t.test(data ~ groups, data = subset(longCSVlik, groups %in% c("B_fear_Csmi", "B_fear_Csmv")), paired=TRUE)
cohens_d(longCSVlik$data[longCSVlik$groups == "B_fear_Csmi"], longCSVlik$data[longCSVlik$groups == "B_fear_Csmv"], paired = TRUE)
```


## Imagery Acquisition Additional follow-ups (Set A)

### CS+s
```{r}
t.test(data ~ groups, data = subset(longCSVlik, groups %in% c("A_fear_Cspv", "A_fear_Cspi")), paired=TRUE)
cohens_d(longCSVlik$data[longCSVlik$groups == "A_fear_Cspv"], longCSVlik$data[longCSVlik$groups == "A_fear_Cspi"], paired = TRUE)
```

### CS-s
```{r}
t.test(data ~ groups, data = subset(longCSVlik, groups %in% c("A_fear_Csmv", "A_fear_Csmi")), paired=TRUE)
cohens_d(longCSVlik$data[longCSVlik$groups == "A_fear_Csmv"], longCSVlik$data[longCSVlik$groups == "A_fear_Csmi"], paired = TRUE)
```

## Across Phase Analyses

### CS+s
Acquiring fear to an imagined vs a viewed stimulus
```{r}
t.test(data ~ groups, data = subset(longCSVlik, groups %in% c("A_fear_Cspi", "B_fear_Cspv")), paired=TRUE)
cohens_d(longCSVlik$data[longCSVlik$groups == "A_fear_Cspi"], longCSVlik$data[longCSVlik$groups == "B_fear_Cspv"], paired = TRUE)
```

Generalized fear to an imagined vs a viewed stimulus
```{r}
t.test(data ~ groups, data = subset(longCSVlik, groups %in% c("B_fear_Cspi", "A_fear_Cspv")), paired=TRUE)
cohens_d(longCSVlik$data[longCSVlik$groups == "B_fear_Cspi"], longCSVlik$data[longCSVlik$groups == "A_fear_Cspv"], paired = TRUE)
```

Fear acquired to a viewed stimulus vs fear generalized to a viewed stimulus
```{r}
t.test(data ~ groups, data = subset(longCSVlik, groups %in% c("A_fear_Cspv", "B_fear_Cspv")), paired=TRUE)
cohens_d(longCSVlik$data[longCSVlik$groups == "A_fear_Cspv"], longCSVlik$data[longCSVlik$groups == "B_fear_Cspv"], paired = TRUE)
```

Fear acquired to an imagined stimulus vs fear generalized to an imagined stimlus
```{r}
t.test(data ~ groups, data = subset(longCSVlik, groups %in% c("A_fear_Cspi", "B_fear_Cspi")), paired=TRUE)
cohens_d(longCSVlik$data[longCSVlik$groups == "A_fear_Cspi"], longCSVlik$data[longCSVlik$groups == "B_fear_Cspi"], paired = TRUE)
```


### CS-s 
Acquired percept modalities (CS- imagine Set A vs CS- view Set B)
```{r}
t.test(data ~ groups, data = subset(longCSVlik, groups %in% c("A_fear_Csmi", "B_fear_Csmv")), paired=TRUE)
cohens_d(longCSVlik$data[longCSVlik$groups == "A_fear_Csmi"], longCSVlik$data[longCSVlik$groups == "B_fear_Csmv"], paired = TRUE)
```

Generalized percept modalities (CS- imagine Set B vs CS- view Set A)
```{r}
t.test(data ~ groups, data = subset(longCSVlik, groups %in% c("B_fear_Csmi", "A_fear_Csmv")), paired=TRUE)
cohens_d(longCSVlik$data[longCSVlik$groups == "B_fear_Csmi"], longCSVlik$data[longCSVlik$groups == "A_fear_Csmv"], paired = TRUE)
```

Viewed CS-s
```{r}
t.test(data ~ groups, data = subset(longCSVlik, groups %in% c("A_fear_Csmv", "B_fear_Csmv")), paired=TRUE)
cohens_d(longCSVlik$data[longCSVlik$groups == "A_fear_Csmv"], longCSVlik$data[longCSVlik$groups == "B_fear_Csmv"], paired = TRUE)
```

Imagined CS-s
```{r}
t.test(data ~ groups, data = subset(longCSVlik, groups %in% c("A_fear_Csmi", "B_fear_Csmi")), paired=TRUE)
cohens_d(longCSVlik$data[longCSVlik$groups == "A_fear_Csmi"], longCSVlik$data[longCSVlik$groups == "B_fear_Csmi"], paired = TRUE)
```

### Vividness ANOVA
Does the vividness from the self-report questionnaire impact ratings?
```{r, include=FALSE}
longviv <- CSV %>% select("Subject_ID", "B_vivid_Cspi", "B_vivid_Csmi", "A_vivid_Cspi", "A_vivid_Csmi") %>%
  pivot_longer(cols = c("B_vivid_Cspi", "B_vivid_Csmi", "A_vivid_Cspi", "A_vivid_Csmi"), names_to = "groups", values_to = "data") %>%
  mutate(CS = case_when(grepl("Csp", groups) ~ "CSP",
                        grepl("Csm", groups) ~ "CSM")) %>%
  mutate(Phase = case_when(startsWith(groups, "A") ~ "A",
                           startsWith(groups, "B") ~ "B"))
```

```{r vivid aov, echo = FALSE}
vividanov <- ezANOVA(data=longviv, dv = .(data), wid = .(Subject_ID), within = .(CS, Phase), type = 2, detailed = TRUE)
print(vividanov)

table7 <- apa.ezANOVA.table(vividanov, table.number = 7, filename = "vividnessanova.doc")
```


### Vividness t-test
Is the average vividness greater than no visualizations?
```{r vivid t}
vivavg <- CSV %>% select("Subject_ID", "B_vivid_Cspi", "B_vivid_Csmi", "A_vivid_Cspi", "A_vivid_Csmi") %>% rowwise() %>%
  mutate(avg = mean(c(B_vivid_Cspi, B_vivid_Csmi, A_vivid_Cspi, A_vivid_Csmi)))

t.test(vivavg$avg, mu = 1, alternative = "two.sided")
cohens_d(vivavg$avg)
```

\pagebreak
# Skin Conductance Response (SCR)
``` {r include = FALSE}
CSVall <- subset(CSV, select = c("Subject_ID", "GSR_A_cCspv", "GSR_A_cCsmv", "GSR_A_cCspi", "GSR_A_cCsmi", "GSR_B_cCspv", "GSR_B_cCsmv", "GSR_B_cCspi", "GSR_B_cCsmi")) 

## Edit look of database (melt function allows ANOVA to be run)
longfctm.complete <- melt(CSVall, id = "Subject_ID", measured = c("GSR_A_cCspv", "GSR_A_cCsmv", "GSR_A_cCspi", "GSR_A_cCsmi", "GSR_B_cCspv", "GSR_B_cCsmv", "GSR_B_cCspi", "GSR_B_cCsmi"))
names(longfctm.complete) <- c("Participant", "groups", "data")
longfctm.complete$CS <- gl(2, 33, labels = c("CSP", "CSM"))
longfctm.complete$Percept <- gl(2, 66, labels = c("View", "Imagine"))
longfctm.complete$Phase <- gl(2, 132, labels = c("A", "B"))
```

## Descriptive Statistics
```{r echo = FALSE}
stat.desc(CSVall)
```

## 2x2x2 ANOVA
```{r 2x2x2 gsr}
anovatbl <- ezANOVA(data=longfctm.complete, dv = .(data), wid = .(Participant), within = .(CS, Percept, Phase), type = 2, detailed = TRUE)
print(anovatbl)

table2 <- apa.ezANOVA.table(anovatbl, table.number = 2, filename = "gsranova.doc")
```

### Visual Acquisition (Set B)
```{r echo = FALSE}
setB <- subset(CSV, select = c("Subject_ID", "GSR_B_cCspv", "GSR_B_cCsmv", "GSR_B_cCspi", "GSR_B_cCsmi"))
longB <- melt(setB, id = "Subject_ID", measured = c("GSR_B_cCspv", "GSR_B_cCsmv", "GSR_B_cCspi", "GSR_B_cCsmi"))
names(longB) <- c("Participant", "groups", "data")
longB$CS <- gl(2, 33, labels = c("CSP", "CSM"))
longB$Percept <- gl(2, 66, labels = c("View", "Imagine"))


bgsrv <- ggplot(longB, aes(CS, data, fill= CS)) 
bgsrv <- bgsrv + theme_bw() + stat_summary(fun = mean, geom = "bar", colour="Black") +  stat_summary(fun.data =mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .35) + scale_x_discrete(breaks=c("CSP","CSM"), labels = c("CS+","CS-")) + scale_fill_manual(values=c("#D43F3A", "#357EBD")) + ggtitle("Visual Acquisition Phase") + theme(plot.title = element_text(size=14, hjust = .5), axis.title.x = element_blank(), axis.title.y = element_blank(), legend.position = "none", text = element_text(size=20)) + facet_grid(cols = vars(Percept)) + geom_jitter(width = .15, color = "gray36")
bgsrv

ggsave(filename = "GSR_VisAcq.tiff", plot = bgsrv, height = 12, width = 11.6, units = "cm", device='tiff', dpi=300)
```

### Imagery Acquisition (Set A)
```{r, echo = FALSE}
setA <- subset(CSV, select = c("Subject_ID", "GSR_A_cCspv", "GSR_A_cCsmv", "GSR_A_cCspi", "GSR_A_cCsmi"))
longA <- melt(setA, id = "Subject_ID", measured = c("GSR_A_cCspv", "GSR_A_cCsmv", "GSR_A_cCspi", "GSR_A_cCsmi"))
names(longA) <- c("Participant", "groups", "data")
longA$CS <- gl(2, 33, labels = c("CSP", "CSM"))
longA$Percept <- gl(2, 66, labels = c("View", "Imagine"))

agsri <- ggplot(longA, aes(CS, data, fill= CS)) 
agsri <- agsri + theme_bw() + stat_summary(fun = mean, geom = "bar", colour="Black") +  stat_summary(fun.data =mean_cl_normal, geom = "errorbar", position = position_dodge(width=.9), width = .35) + scale_x_discrete(breaks=c("CSP","CSM"), labels = c("CS+","CS-")) + scale_fill_manual(values=c("#EEA236", "#46B8DA")) + labs(y = "SCR") + ggtitle("Imagery Acquisition Phase") + theme(plot.title = element_text(size=14, hjust = .5), axis.title.x = element_blank(), legend.position = "none", text = element_text(size=20)) + facet_grid(~factor(Percept, levels=rev(unique(longA$Percept)))) + geom_jitter(width = .15, color = "gray36")
agsri

ggsave(filename = "GSR_ImgAcq.tiff", plot = agsri, height = 12, width = 11.6, units = "cm", device='tiff', dpi=300)
```

\pagebreak
# Three-way ANOVA Skin Conductance Follow-up tests

## Visual Acquisition Primary Analyses (Set B)

### Fear View
```{r}
t.test(data ~ groups, data = subset(longB, groups %in% c("GSR_B_cCspv", "GSR_B_cCsmv")), paired=TRUE)
cohens_d(longB$data[longB$groups == "GSR_B_cCspv"], longB$data[longB$groups == "GSR_B_cCsmv"], paired = TRUE)
```

#### Bayesian Test
```{r, echo = FALSE}
comp <- csCompare(CSV$GSR_B_cCspv, CSV$GSR_B_cCsmv)
comp
interpret_bf(comp$bayes.results$bf10, include_value = TRUE)
```

Sensitivity + Robustness
```{r, echo = FALSE}
sens <- csSensitivity(CSV$GSR_B_cCspv, CSV$GSR_B_cCsmv)
sens
csRobustnessPlot(CSV$GSR_B_cCspv, CSV$GSR_B_cCsmv, BF01 = TRUE)
```


### Generalized Fear to Imagine
```{r}
t.test(data ~ groups, data = subset(longB, groups %in% c("GSR_B_cCspi", "GSR_B_cCsmi")), paired=TRUE)
cohens_d(longB$data[longB$groups == "GSR_B_cCspi"], longB$data[longB$groups == "GSR_B_cCsmi"], paired = TRUE)
```

#### Bayesian Test
```{r, echo = FALSE}
compi <- csCompare(CSV$GSR_B_cCspi, CSV$GSR_B_cCsmi)
compi
interpret_bf(compi$bayes.results$bf10, include_value = TRUE)
```

Sensitivity + Robustness
```{r, echo = FALSE}
sens <- csSensitivity(CSV$GSR_B_cCspi, CSV$GSR_B_cCsmi)
print(sens)
csRobustnessPlot(CSV$GSR_B_cCspi, CSV$GSR_B_cCsmi, BF01 = TRUE)
```

## Imagery Acquisition Primary Analyses (Set A)

### Fear Imagine
```{r}
t.test(data ~ groups, data = subset(longA, groups %in% c("GSR_A_cCspi", "GSR_A_cCsmi")), paired=TRUE)
cohens_d(longA$data[longA$groups == "GSR_A_cCspi"], longA$data[longA$groups == "GSR_A_cCsmi"], paired = TRUE)
```

#### Bayesian Test
```{r, echo = FALSE}
compi <- csCompare(CSV$GSR_A_cCspi, CSV$GSR_A_cCsmi)
compi
interpret_bf(compi$bayes.results$bf10, include_value = TRUE)
```

Sensitivity + Robustness
```{r, echo = FALSE}
sensi <- csSensitivity(CSV$GSR_A_cCspi, CSV$GSR_A_cCsmi)
print(sensi)
csRobustnessPlot(CSV$GSR_A_cCspi, CSV$GSR_A_cCsmi, BF01 = TRUE)
```

### Generalized Fear to View
```{r}
t.test(data ~ groups, data = subset(longA, groups %in% c("GSR_A_cCspv", "GSR_A_cCsmv")), paired=TRUE)
cohens_d(longA$data[longA$groups == "GSR_A_cCspv"], longA$data[longA$groups == "GSR_A_cCsmv"], paired = TRUE)
```

#### Bayesian Test
```{r, echo = FALSE}
comp <- csCompare(CSV$GSR_A_cCspv, CSV$GSR_A_cCsmv)
comp
interpret_bf(comp$bayes.results$bf10, include_value = TRUE)
```

Sensitivity + Robustness
```{r, echo = FALSE}
sens <- csSensitivity(CSV$GSR_A_cCspv, CSV$GSR_A_cCsmv)
print(sens)
csRobustnessPlot(CSV$GSR_A_cCspv, CSV$GSR_A_cCsmv, BF01 = TRUE)
```

## Visual Acquisition Additional follow-ups (Set B)

### CS+s
```{r}
t.test(data ~ groups, data = subset(longfctm.complete, groups %in% c("GSR_B_cCspi", "GSR_B_cCspv")), paired=TRUE)
cohens_d(longfctm.complete$data[longfctm.complete$groups == "GSR_B_cCspi"], longfctm.complete$data[longfctm.complete$groups == "GSR_B_cCspv"], paired = TRUE)
```

### CS-s 
```{r}
t.test(data ~ groups, data = subset(longfctm.complete, groups %in% c("GSR_B_cCsmi", "GSR_B_cCsmv")), paired=TRUE)
cohens_d(longfctm.complete$data[longfctm.complete$groups == "GSR_B_cCsmi"], longfctm.complete$data[longfctm.complete$groups == "GSR_B_cCsmv"], paired = TRUE)
```


## Imagery Acquisition Additional follow-ups (Set A)

### CS+s
```{r}
t.test(data ~ groups, data = subset(longfctm.complete, groups %in% c("GSR_A_cCspi", "GSR_A_cCspv")), paired=TRUE)
cohens_d(longfctm.complete$data[longfctm.complete$groups == "GSR_A_cCspi"], longfctm.complete$data[longfctm.complete$groups == "GSR_A_cCspv"], paired = TRUE)
```

### CS-s
```{r}
t.test(data ~ groups, data = subset(longfctm.complete, groups %in% c("GSR_A_cCsmi", "GSR_A_cCsmv")), paired=TRUE)
cohens_d(longfctm.complete$data[longfctm.complete$groups == "GSR_A_cCsmi"], longfctm.complete$data[longfctm.complete$groups == "GSR_A_cCsmv"], paired = TRUE)
```

## Across Phase Analyses

### CS+s
Acquiring fear to an imagined vs a viewed stimulus
```{r}
t.test(data ~ groups, data = subset(longfctm.complete, groups %in% c("GSR_A_cCspi", "GSR_B_cCspv")), paired=TRUE)
cohens_d(longfctm.complete$data[longfctm.complete$groups == "GSR_A_cCspi"], longfctm.complete$data[longfctm.complete$groups == "GSR_B_cCspv"], paired = TRUE)
```

Generalized fear to an imagined vs a viewed stimulus
```{r}
t.test(data ~ groups, data = subset(longfctm.complete, groups %in% c("GSR_B_cCspi", "GSR_A_cCspv")), paired=TRUE)
cohens_d(longfctm.complete$data[longfctm.complete$groups == "GSR_B_cCspi"], longfctm.complete$data[longfctm.complete$groups == "GSR_A_cCspv"], paired = TRUE)
```

Fear acquired to a viewed stimulus vs fear generalized to a viewed stimulus
```{r}
t.test(data ~ groups, data = subset(longfctm.complete, groups %in% c("GSR_A_cCspv", "GSR_B_cCspv")), paired=TRUE)
cohens_d(longfctm.complete$data[longfctm.complete$groups == "GSR_A_cCspv"], longfctm.complete$data[longfctm.complete$groups == "GSR_B_cCspv"], paired = TRUE)
```

Fear acquired to an imagined stimulus vs fear generalized to an imagined stimulus
```{r}
t.test(data ~ groups, data = subset(longfctm.complete, groups %in% c("GSR_A_cCspi", "GSR_B_cCspi")), paired=TRUE)
cohens_d(longfctm.complete$data[longfctm.complete$groups == "GSR_A_cCspi"], longfctm.complete$data[longfctm.complete$groups == "GSR_B_cCspi"], paired = TRUE)
```


### CS-s 
Acquired percept modalities (CS- imagine Set A vs CS- view Set B)
```{r}
t.test(data ~ groups, data = subset(longfctm.complete, groups %in% c("GSR_A_cCsmi", "GSR_B_cCsmv")), paired=TRUE)
cohens_d(longfctm.complete$data[longfctm.complete$groups == "GSR_A_cCsmi"], longfctm.complete$data[longfctm.complete$groups == "GSR_B_cCsmv"], paired = TRUE)
```

Generalized percept modalities (CS- imagine Set B vs CS- view Set A)
```{r}
t.test(data ~ groups, data = subset(longfctm.complete, groups %in% c("GSR_B_cCsmi", "GSR_A_cCsmv")), paired=TRUE)
cohens_d(longfctm.complete$data[longfctm.complete$groups == "GSR_B_cCsmi"], longfctm.complete$data[longfctm.complete$groups == "GSR_A_cCsmv"], paired = TRUE)
```

Viewed CS-s
```{r}
t.test(data ~ groups, data = subset(longfctm.complete, groups %in% c("GSR_A_cCsmv", "GSR_B_cCsmv")), paired=TRUE)
cohens_d(longfctm.complete$data[longfctm.complete$groups == "GSR_A_cCsmv"], longfctm.complete$data[longfctm.complete$groups == "GSR_B_cCsmv"], paired = TRUE)
```

Imagined CS-s
```{r}
t.test(data ~ groups, data = subset(longfctm.complete, groups %in% c("GSR_A_cCsmi", "GSR_B_cCsmi")), paired=TRUE)
cohens_d(longfctm.complete$data[longfctm.complete$groups == "GSR_A_cCsmi"], longfctm.complete$data[longfctm.complete$groups == "GSR_B_cCsmi"], paired = TRUE)
```

\pagebreak
# Pretty Correlation Graphs for Funsies

## Visual Acquisition 
```{r, include=FALSE}
CSVcorr <- CSV %>% select("Subject_ID", "GSR_B_cCspv", "GSR_B_cCsmv", "GSR_B_cCspi", "GSR_B_cCsmi", "B_fear_Cspv", "B_fear_Csmv", "B_fear_Cspi", "B_fear_Csmi", "B_vivid_Cspi", "B_vivid_Csmi", "B_effort_Cspi", "B_effort_Csmi","TAI_Score", "SAI_Score", "Attentional_Control", "VVIQ_Score") %>%
  rowwise() %>%
  mutate(gsrviewdiff = GSR_B_cCspv - GSR_B_cCsmv,
         gsrimagdiff = GSR_B_cCspi - GSR_B_cCsmi,
         likviewdiff = B_fear_Cspv - B_fear_Csmv,
         likimagdiff = B_fear_Cspi - B_fear_Csmi,
         vivid_avg = mean(c(B_vivid_Cspi, B_vivid_Csmi)),
         effort_avg = mean(c(B_effort_Cspi, B_effort_Csmi))) %>%
  select("gsrviewdiff", "gsrimagdiff", "likviewdiff", "likimagdiff", 
         "vivid_avg", "effort_avg", "TAI_Score", "SAI_Score",
         "Attentional_Control", "VVIQ_Score") %>%
  dplyr::rename("SCR View Differential Fear" = gsrviewdiff, 
         "SCR Imagine Differential Fear" = gsrimagdiff, 
         "Self Report View Differential Fear" = likviewdiff, 
         "Self Report Imagine Differential Fear" = likimagdiff,
         "Self Report Vividness" = vivid_avg, 
         "Self Report Effort" = effort_avg, 
         "Trait Anxiety" = TAI_Score, 
         "State Anxiety" = SAI_Score, 
         "Attentional Control" = Attentional_Control,
         "Visual Vividness (VVIQ)" = VVIQ_Score)
corrs <- cor(na.omit(CSVcorr))
pvals <- cor_pmat(CSVcorr)

```

```{r}
col1 <- colorRampPalette(c("#357EBDFF", "#46B8DAFF", "#5CB85CFF", "#EEA236FF", "#D43F3AFF"))

corrplot(corrs, cl.ratio = .19, type = "upper", tl.cex = .8, tl.col = "black", diag = FALSE, number.cex = .6, p.mat = pvals, insig = "label_sig", sig.level = c(.001, 0.01, .05), pch.cex = .9, col = col1(10))
```

## Imagery Acquisition
```{r, include=FALSE}
CSVcorr <- subset(CSV, select = c("Subject_ID", "GSR_A_cCspv", "GSR_A_cCsmv", "GSR_A_cCspi", "GSR_A_cCsmi", "A_fear_Cspv", "A_fear_Csmv", "A_fear_Cspi", "A_fear_Csmi")) 
CSVlikA <- subset(CSV, select = c("Subject_ID", "A_vivid_Cspi", "A_vivid_Csmi", "A_effort_Cspi", "A_effort_Csmi"))

CSVcorrdiff <- data.frame(Subject_ID = CSVcorr$Subject_ID)

CSVcorrdiff$gsrviewdiff <- CSVcorr$GSR_A_cCspv - CSVcorr$GSR_A_cCsmv
CSVcorrdiff$gsrimagdiff <- CSVcorr$GSR_A_cCspi - CSVcorr$GSR_A_cCsmi
CSVcorrdiff$likviewdiff <- CSVcorr$A_fear_Cspv - CSVcorr$A_fear_Csmv
CSVcorrdiff$likimagdiff <- CSVcorr$A_fear_Cspi - CSVcorr$A_fear_Csmi

other <- subset(CSV, select = c("Subject_ID", "TAI_Score", "SAI_Score", "Attentional_Control", "VVIQ_Score"))
CSVcorrdiff <- merge(CSVcorrdiff, other, by = "Subject_ID")

vviq <- subset(CSV, select = c("Subject_ID", "VVIQ_Score"))
CSVlikA$A_vivid_avg <- rowMeans(CSVlikA[ , (c("A_vivid_Cspi", "A_vivid_Csmi"))])
CSVlikA$A_effort_avg <- rowMeans(CSVlikA[ , (c("A_effort_Cspi", "A_effort_Csmi"))])
lik <- subset(CSVlikA, select = c("Subject_ID", "A_vivid_avg", "A_effort_avg"))

CSVcorrdiff <- merge(CSVcorrdiff, lik, by = "Subject_ID")

CSVcorrdiff <- subset(CSVcorrdiff, select = -c(Subject_ID))

corrdiff <- cor(na.omit(CSVcorrdiff))
pvaldiff <- cor_pmat(corrdiff)

```


```{r include = FALSE}
colnames(corrdiff) <- c("View Difference-SCR", "Imagine Difference-SCR", "View Difference- Self-Report", "Imagine Difference- Self-Report", "Trait Anxiety Inventory", "State Anxiety Inventory", "Attentional Control", "VVIQ", "Self-Reported Vividness", "Self-Reported Effort")

rownames(corrdiff) <- c("View Difference-SCR", "Imagine Difference-SCR", "View Difference- Self-Report", "Imagine Difference- Self-Report", "Trait Anxiety Inventory", "State Anxiety Inventory", "Attentional Control", "VVIQ", "Self-Reported Vividness", "Self-Reported Effort")

colnames(pvaldiff) <- c("View Difference-SCR", "Imagine Difference-SCR", "View Difference- Self-Report", "Imagine Difference- Self-Report", "Trait Anxiety Inventory", "State Anxiety Inventory", "Attentional Control", "VVIQ", "Self-Reported Vividness", "Self-Reported Effort")

rownames(pvaldiff) <- c("View Difference-SCR", "Imagine Difference-SCR", "View Difference- Self-Report", "Imagine Difference- Self-Report", "Trait Anxiety Inventory", "State Anxiety Inventory", "Attentional Control", "VVIQ", "Self-Reported Vividness", "Self-Reported Effort")

```


```{r}
col1 <- colorRampPalette(c("#357EBDFF", "#46B8DAFF", "#5CB85CFF", "#EEA236FF", "#D43F3AFF"))

corrplot(corrdiff, cl.ratio = .19, type = "upper", tl.cex = .8, tl.col = "black", diag = FALSE, number.cex = .6, p.mat = pvaldiff, insig = "label_sig", sig.level = c(.001, 0.01, .05), pch.cex = .9, col = col1(10))
```
